Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-08 paper/paper.tex
Why we need to reevaluate

Previous experimental evaluations have used weak maximum clique algorithms, or even enumeration
algorithms---for example, Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} compare a modified form
of the Bron-Kerbosch maximal clique enumeration algorithm \cite{Bron:1973:AFC:362342.362367} with a
CP optimisation approach. Our experience suggests that the optimisation form of the clique problem
is often many orders of magnitude easier than enumeration, due to the possibility of employing a
strong bound function to prune the search space.  Therefore, in \cref{eval1}, we  re-evaluate the
clique-based approach using a modern algorithm, and we show that it outperforms CP on labelled
graphs, and that it is competitive with CP on unlabelled graphs.

@@

Previous experimental evaluations of the association graph model have used either maximal clique
enumeration algorithms \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08} (even when the
maximisation problem was being considered), or very simple maximum clique algorithms
\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}. Thus we re-evaluate the approach
using a modern maximum clique algorithm. Association graphs are dense, even if the input is sparse,
so we will using (the single-threaded, bit-parallel version of) the maximum clique solver by
McCreesh and Prosser \cite{DBLP:journals/topc/McCreeshP15}, which implements Prosser's
\cite{DBLP:journals/algorithms/Prosser12} ``MCSa1'' variant of a series of algorithms due to Tomita
\textit{et al.}\
\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
bitset encoding due to San Segundo \textit{et al.}\
\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the
``FC+Bound'' and ``MAC+Bound'' (simply referred to as FC and MAC) CP implementations of Ndiaye and
Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on machines with Intel Xeon
E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and a timeout of one hour was
used.

>>>>

Previous experimental evaluations have used simple maximum clique algorithms, or even enumeration
algorithms---for example, Vismara and Valery \cite{DBLP:conf/mco/VismaraV08} compare a modified form
of the Bron-Kerbosch maximal clique enumeration algorithm \cite{Bron:1973:AFC:362342.362367} with a
CP optimisation approach. Our experience suggests that a modern maximum clique algorithm could give
many orders of magnitude improvement, due to a strong bound function which prunes the search space.
Therefore, in \cref{eval1}, we re-evaluate the clique-based approach using a modern algorithm, and
we show that it outperforms CP on labelled graphs, and that it is competitive with CP on unlabelled
graphs, contradicting earlier conclusions.

@@

Previous experimental evaluations of the association graph model have used either maximal clique
enumeration algorithms \cite{DBLP:journals/tcs/Koch01,DBLP:conf/mco/VismaraV08} (even when the
maximisation problem was being considered), or very simple maximum clique algorithms
\cite{DBLP:conf/sspr/BunkeFGSV02,DBLP:journals/jgaa/ConteFV07}, and so their conclusions may now be
overly pessimistic. Thus we re-evaluate the approach using a modern maximum clique algorithm.
Association graphs are dense, even if the input is sparse, so we will using (the single-threaded,
bit-parallel version of) the maximum clique solver by McCreesh and Prosser
\cite{DBLP:journals/topc/McCreeshP15}, which implements Prosser's
\cite{DBLP:journals/algorithms/Prosser12} ``MCSa1'' variant of a series of algorithms due to Tomita
\textit{et al.}\
\cite{DBLP:conf/dmtcs/TomitaS03,DBLP:journals/jgo/TomitaK07,DBLP:conf/walcom/TomitaSHTW10}, using a
bitset encoding due to San Segundo \textit{et al.}\
\cite{DBLP:journals/cor/SegundoRJ11,DBLP:journals/ol/SegundoMRH13}. We compare this to the
``FC+Bound'' and ``MAC+Bound'' (simply referred to as FC and MAC) CP implementations of Ndiaye and
Solnon \cite{DBLP:conf/cp/NdiayeS11}.  We perform our experiments on machines with Intel Xeon
E5-2640 v2 CPUs and 64GBytes RAM; software was compiled using GCC 4.9, and a timeout of one hour was
used.
